Modeling the uncertainties of solar-system ephemerides for robust gravitational-wave searches with pulsar timing arrays

### 2020-01-02 paper/contrib.tex
Edits to paper after comments
Arxiv submission

% !TEX root = nanograv_11yr_cw.tex
This document is the result of more than a decade of work by the entire NANOGrav collaboration.
We acknowledge specific contributions below.
Z.A., K.C., P.B.D., M.E.D., T.D., J.A.E., R.D.F., E.C.F., E.F., P.A.G., G.J., M.L.J., M.T.L., L.L., D.R.L., R.S.L., M.A.M., C.N., D.J.N., T.T.P., S.M.R., P.S.R., R.S., I.H.S., K.S., J.K.S., and W.W.Z. developed the 11-year data set.
M.V.\ led this analysis and coordinated the paper writing.
M.V., S.R.T., and J.S. developed \textsc{BayesEphem}, managed Bayesian-inference runs, and performed data analysis, with help from C.C., J.A.E., T.J.W.L., and S.J.V. Ephemeris data and expertise were provided by W.M.F.\ and R.S.P.

>>>>

% !TEX root = nanograv_11yr_cwtex
This document is the result of more than a decade of work by the entire NANOGrav collaboration.
We acknowledge specific contributions below.
ZA, KC, PBD, MED, TD, JAE, RDF, ECF, EF, PAG, GJ, MLJ, MTL, LL, DRL, RSL, MAM, CN, DJN, TTP, SMR, PSR, RS, IHS, KS, JKS, and WWZ developed the 11-year data set.
MV\ led this analysis and coordinated writing.
MV, SRT, and JS developed \textsc{BayesEphem}, managed Bayesian-inference runs, and performed data analysis, with help from CC, JAE, TJWL, and SJV.
MV, SRT, and JS wrote this article, with edits by DJN, MTL, TJWL, DLK, JSH, and SJV.
Ephemeris data and expertise were provided by WMF and RSP.
